Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-25 paper/ICPC19/icpc19.tex
language chart
adding more to S3.B
check todo
paper update
shorten SIG's website

In this section, the methodology used to measure the impact of security refactorings on the maintainability of open-source software is presented in depth in the following sections and illustrated in Figure \ref{fig:met}. Aiming to answer the research questions presented in this paper, we use a dataset containing more than 700 security refactorings collected from open-source software available on GitHub and where 648 were reported in a previous study conducted in 2017 \cite{Reis:2017:IJSSE}. In parallel, a baseline of regular commits was randomly collected from the list of projects of the main dataset to evaluate what is the impact of regular commits on the maintainability of open-source software. The Software Improvement Group's\footnote{SIG's website is available at https://www.softwareimprovementgroup.com/ (Accessed on January 23, 2019)} web-based source code analysis service Better Code Hub (BCH) \footnote{BCH's website is available at https://bettercodehub.com/ (Accessed on January 23, 2019)} was used to collect the maintainability reports for both security and regular commits.

@@

@@

\subsection{Security vs. Baseline Commits}

The baseline dataset uses the security commits dataset as input. For each security commit, one random commit is selected from the list of all commits of the belonging project. We originate the regular commits from the security commits to ensure that differences in maintainability are not consequence of characteristics
of different projects.

\subsection{Maintainability Analysis}

>>>>

In this section, the methodology used to measure the impact of security refactorings on the maintainability of open-source software is presented in depth in the following sections and illustrated in Figure \ref{fig:met}. Aiming to answer the research questions presented in this paper, we use a dataset containing more than 700 security refactorings collected from open-source software available on GitHub and where 648 were reported in a previous study conducted in 2017 \cite{Reis:2017:IJSSE}. In parallel, a baseline of regular commits was randomly collected from the list of projects of the main dataset to evaluate what is the impact of regular commits on the maintainability of open-source software. The Software Improvement Group's\footnote{SIG's website is available at https://www.sig.eu/ (Accessed on January 23, 2019)} web-based source code analysis service Better Code Hub (BCH) \footnote{BCH's website is available at https://bettercodehub.com/ (Accessed on January 23, 2019)} was used to collect the maintainability reports for both security and regular commits.

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/language_dist.pdf}
 	\caption{Language Distribution}
	\label{fig:lang}
\end{figure}

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/type_dist.pdf}
 	\caption{Type Distribution}
	\label{fig:type}
\end{figure}

@@

\subsection{Security vs. Baseline Commits}
%
Although we want to assess the maintainability of security-related commits,
\textcolor{mypink3}{there is no evidence in previous work on the impact of \textit{regular} commits
in the maintainability of projects}. Thus, we analyze the maintainability of
regular commits and use them as a baseline.

The baseline dataset uses the security commits dataset as input. For each
security commit, one random commit is selected from the list of all commits of
the belonging project. We originate the regular commits from the security
commits to ensure that differences in maintainability are not consequence of
characteristics of different projects.
%
\subsection{Maintainability Analysis}
